A new breeding crossover approach for evolutionary algorithms

### 2023-09-20 paper.tex
Conclusion Update

@@

    In this document, we propose a different technique to the canonical approach One Point Crossover, where part of the genetic information is copied directly to each of the offspring in the crossover operator, where this type of crossover may perform inadequately in continuous optimization problems. Figure~\ref{fig.onepoint_crossover} provides an example of the One Point Crossover.

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.70\linewidth]{img/fig_onepoint_crossover.pdf}
        \caption{Classical approach example for the One Point Crossover, with crossover point 3.} \label{fig.onepoint_crossover}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.70\linewidth]{img/fig_contrange_crossover.pdf}
        \caption{Our proposal example for the Continuous Range Crossover mating the same couple of individuals.} \label{fig.contrange_crossover}
        \end{figure}

@@

    To validate our research, we performed the statistical Z-Test with a ninety-five percent confidence level to analyze the alternatives we present in this proposal. In the ten-dimension category, we found that One Point crossover was the better alternative on four occasions, while our Continuous Range proposal was better on twelve other functions out of thirty. For the thirty-dimensions category, the One Point crossover was better on five occasions, while the Continuous Range crossover was the best alternative on another thirteen. Our experiment results confirm that our solution can be considered a adequate alternative.

@@

\begin{acknowledgement}
    This paper has been supported in part by TecNM Project 15340.22-P.
\end{acknowledgement}

>>>>

    One of the most important contributions of this research is that it proposes a new crossing alternative for the reproduction of individuals in a population. This strategy is practical in evolutionary algorithms where the individual's information has a structure similar to the genetic code's. With some tinkering, this strategy could be valuable in other algorithms\cite{venter2003particle,wang2018particle}, such as Particle Swarm Optimization (PSO).

@@

    In this document, we propose a different technique to the canonical approach One Point Crossover, where part of the genetic information is copied directly to each offspring in the crossover operator. This type of crossover may fail to perform successfully in continuous optimization problems. Figure~\ref{fig.onepoint_crossover} provides an example of the One Point Crossover.

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.50\linewidth]{img/fig_onepoint_crossover.pdf}
        \caption{Classical approach example for the One Point Crossover, with crossover point 3.} \label{fig.onepoint_crossover}
        \end{figure}

@@

    \begin{figure}[!ht]
        \centering
        \includegraphics[width=0.50\linewidth]{img/fig_contrange_crossover.pdf}
        \caption{Our proposal example for the Continuous Range Crossover mating the same couple of individuals.} \label{fig.contrange_crossover}
        \end{figure}

@@

    To validate our research, we performed the statistical Z-Test with a ninety-five percent confidence level to analyze the alternatives we present in this proposal. In the ten-dimension category, we found that One Point crossover was the better alternative on four occasions, while our Continuous Range proposal was better on twelve other functions out of thirty. For the thirty-dimensions category, the One Point crossover was better on five occasions, while the Continuous Range crossover was the best alternative on another thirteen. Our experiment results confirm that our solution can be considered an adequate alternative.

@@

    Based on the analysis of our results, we have shown that the proposed crossover alternative for the reproduction of individuals in a population obtains good results. Therefore, it can be valuable in other evolutionary algorithms where the information of individuals has a structure similar to that of the genetic code. However, with some adaptation, it could be helpful in different types of algorithms, such as Particle Swarm Optimization. In future work, we could investigate a combination between the canonical One Point Crossover strategy and randomly alternating with the proposed Continuous Range Crossover.

\begin{acknowledgement}
    This paper has been supported in part by TecNM Project 18186.23-P.
\end{acknowledgement}
